The Impact of Cloud Computing in $10$ Years

### 2013-05-04 essay/main.tex
write essay

\documentclass[11pt, times]{article}
\usepackage{cite}
\usepackage[top=1in, bottom=0.75in, left=0.75in, right=0.75in]{geometry}
%\usepackage{pslatex}

@@

\begin{abstract}
Cloud computing has been very active in both academia and industry field for several years. Major cloud computing vendors, like Amazon, Google and Dropbox, have provided users and businesses many advantages such as reliable and convenient storage, elastic computing power, and simple application deployment, lower IT infrastructure cost, etc. In $10$ years, I will expect cloud computing's influence far beyond the current achievements, but deeply inside mobile technology, scientific computing, massive online education and online-to-offline market. In this essay, I will discuss this point with my observations and understandings.
\end{abstract}

>>>>

\documentclass[11pt, journal, onecolumn]{IEEEtran}
\usepackage{cite}
\usepackage{amsmath, amsthm, amsfonts}
\usepackage[top=1in, bottom=0.75in, left=0.75in, right=0.75in]{geometry}

@@

\begin{abstract}
Cloud computing has been very active in both academia and industry field for several years. Major cloud computing vendors, like Amazon, Google and Dropbox, have provided users and businesses many advantages such as reliable and convenient storage, elastic computing power, and simple application deployment, lower IT infrastructure cost, etc. In $10$ years, I will expect cloud computing's influence far beyond the current achievements, but deeply inside mobile technology, massive open online education, online-to-offline business and scientific computing. In this essay, I will discuss this point with my observations and understandings.
\end{abstract}

### 2013-05-04 essay/tex/essay.tex
write essay

\section{Introduction}

\section{Mobile Computing and Cloud Computing}

>>>>

\section{Introduction}
In recent years, cloud computing has provided us with a lot of benefits in many area. Major cloud computing vendors like Amazon, Google and Dropbox have offered the users around the world a cheap, convenient and secure computing and storage resource. For example, Amazon EC2 is one of the most popular cloud computing platform for many companies and individuals. The various types of virtual instances at different price strategies provide very flexible choices for the users. I rent a \emph{m1.micro} instance for the use of my person website and blog for three years at a decent price around $100$ dollas. With the virtual instance, I do not need to install a physical machine at my home and maintain it day by day, which definitely costs more than $100$ dollas for three years.

An additional example of another scenario of cloud computing's application could be cloud storage. Either Dropbox or Google Drive or Amazon Cloud Storage, they provide both companies and individuals cheap and convenient cloud storage which we do not need to worry about the data loss or accessibility. Even though three of them have different data privacy terms, people still quite enjoy this type of services. For example, Dropbox has a marketing plan for university students who has a \emph{.edu} email will obtain an extra $3$GB plus his own $2$GB storage space for free. When I look around with other students, most of them seems to be very happy with the current services. They use Dropbox as a USB drive to share or transfer large amount of data over the air; they also use Dropbox to show pictures or documents during their presentation. Thus, it seeems that the free $5$GB \emph{USB-air-drive} could become more popular and convenient than a $\$10$-$\$15$ USB flash drive.

\section{Mobile and Cloud Computing}
